---
title: "COVID-19 Data Norway"
output:
  html_document
---
<script>
$(document).ready(function(){
$('[data-toggle="tooltip"]').tooltip(); 
});
</script>

<h3 style = "color: #6f7d7e;margin-top:8px;t">Public data about the COVID-19-situation in Norway </h3>
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

### Motivation
The current state of publicly available data about the COVID-19-situtation in Norway is a mix of [PDF-reports](https://www.fhi.no/sv/smittsomme-sykdommer/corona/dags--og-ukerapporter/dags--og-ukerapporter-om-koronavirus/), [Excel-files](https://www.nav.no/no/nav-og-samfunn/statistikk/arbeidssokere-og-stillinger-statistikk/permitterte), [Power BI-dashboards](https://www.helsedirektoratet.no/statistikk/antall-innlagte-pasienter-pa-sykehus-med-pavist-covid-19) and public registries. Further, much of the data is only released as cumulative statistics at aggregated levels (e.g. [MSIS](http://www.msis.no/)). This has created a market for media outlets to release local "situation reports" behind paywalls (see: [Aftenposten](https://www.aftenposten.no/norge/i/K3mnr4/i-det-meste-av-landet-bremser-viruset-opp-i-oslo-sprer-det-seg-raskt-fra-bydel-til-bydel)). The motivation for this project is to collect disparate data sources of Covid-19 in Norway and make them freely available to the public in a timely and coherent manner.

### Contributing to the project
This project is a collaborative and voluntary effort and we would love your help. If you are an individual wishing to contribute, please read the [contribute section](contribute.html). If you are an organization interested in making your data available, please [get in touch](#).

```{r, message=FALSE, warning=FALSE, echo=FALSE}
library(gt)
library(tidyverse)
library(glue)
```

```{r, echo=FALSE}
dl_base     <- "https://raw.githubusercontent.com/thohan88/covid19-nor-data/master/"
pr_base     <- "https://github.com/thohan88/covid19-nor-data/blob/master/"
dl_table    <- function(csv_link, xlsx_link) glue('<a href = "{dl_base}{csv_link}">csv</a> <a href = "{dl_base}{xlsx_link}">xlsx</a>')
dl_map      <- function(geojson) glue('<a href = "{dl_base}{geojson}">geojson</a>')
pr_table    <- function(csv_link) glue('<a href = "{pr_base}{csv_link}"><span class="fa fa-search"></span></a>')
pr_map      <- function(geojson) glue('<a href = "{pr_base}{geojson}"><span class="fa fa-search"></span></a>')

files <- dir("../data", full.names = TRUE, recursive = TRUE) %>% 
  tibble(file_name = .) %>% 
  mutate(file_name_sans_ext = tools::file_path_sans_ext(file_name),
         basename           = basename(file_name_sans_ext), 
         extension          = tools::file_ext(file_name)) %>% 
  mutate(file_name = str_replace_all(file_name, "\\.\\./", "")) %>% 
  spread(extension, file_name) %>% 
  mutate(category = case_when(str_detect(file_name_sans_ext, "/02_maps/")          ~ "Maps",
                              str_detect(file_name_sans_ext, "/01_lookup_tables/") ~ "Lookup tables",
                              str_detect(file_name_sans_ext, "/01_infected/")      ~ "Healthcare",
                              str_detect(file_name_sans_ext, "/02_admissions/")    ~ "Healthcare",
                              str_detect(file_name_sans_ext, "/10_employment/")    ~ "Employment"),
         label    = case_when(str_detect(file_name_sans_ext, "/municipalities$")    ~ "Municipalities",
                              str_detect(file_name_sans_ext, "/municipalities_districts$") ~ "Municipalities and districts",
                              str_detect(file_name_sans_ext, "/msis$")             ~ "MSIS regions",
                              str_detect(file_name_sans_ext, "/02_maps/")          ~ "Maps",
                              str_detect(file_name_sans_ext, "/01_lookup_tables/") ~ "Lookup tables",
                              str_detect(file_name_sans_ext, "/01_infected/")      ~ "Infected",
                              str_detect(file_name_sans_ext, "admissions_with")    ~ "In respirator",
                              str_detect(file_name_sans_ext, "/02_admissions/")    ~ "Admissions",
                              str_detect(file_name_sans_ext, "/10_employment/")    ~ "Employment"),
         source   = case_when(str_detect(file_name_sans_ext, "/01_infected/")      ~ "MSIS",
                              str_detect(file_name_sans_ext, "admissions_with")    ~ "Directorate of Health",
                              str_detect(file_name_sans_ext, "/02_admissions/")    ~ "Directorate of Health",
                              str_detect(file_name_sans_ext, "/10_employment/")    ~ "NAV")) %>% 
  mutate(updated = format(Sys.Date(), "%Y-%m-%d")) %>% 
  #mutate_at(vars(csv, xlsx, geojson), ~paste0("..", .x)) %>% 
  mutate(category = fct_relevel(as.factor(category), "Healthcare", "Lookup tables", "Maps"),
         label    = fct_relevel(as.factor(label), "Infected", "Admissions", "In respirator",
                                "Municipalities", "Municipalities and districts", "MSIS regions"),
         download = case_when(category %in% c("Healthcare", "Employment", "Lookup tables") ~ map2_chr(csv, xlsx, dl_table),
                              category %in% c("Lookup tables", "Maps")                     ~ map_chr(geojson, dl_map)),
         preview  = case_when(category %in% c("Healthcare", "Employment", "Lookup tables") ~ map_chr(csv, pr_table),
                              category %in% c("Lookup tables", "Maps")                     ~ map_chr(geojson, pr_map))) %>% 
  arrange(category, label) %>% 
  filter((label == "Infected" & basename == "municipality_and_district") | label != "Infected") %>% 
  select(category, label, source, updated, download, preview) %>% 
  mutate_at(vars(download, preview), map, htmltools::HTML) %>% 
  mutate_at(vars(category, label), as.character)
```

### Available data

```{r, echo = FALSE}
files %>% 
  filter(category %in% c("Healthcare", "Employment")) %>% 
  gt(groupname_col = "category") %>%
  tab_options(table.width = pct(100),
              table.border.top.style = "hidden",
              table.border.bottom.style = "hidden",
              row.striping.include_table_body = FALSE) %>%
  tab_style(style = list(
    cell_borders(sides = c("top", "bottom"), color = "#DEE2E5", weight = px(1)),
    cell_fill(color = "#ecf0f1")),
    locations = list(cells_row_groups())) %>%
  tab_style(
    style = list(cell_borders(sides = c("top", "bottom"), color = "#DEE2E5", weight = px(1))),
    locations = list(cells_body())) %>%
  cols_label(
    label    = "Name",
    source   = "Source",
    download = "Download",
    updated  = "Updated",
    preview  = "Preview")
```
<br>

### Supporting data

```{r, echo = FALSE}
files %>% 
  filter(category %in% c("Lookup tables", "Maps")) %>% 
  select(category, label, download, preview) %>% 
  gt(groupname_col = "category") %>%
  tab_options(table.width = pct(100),
              table.border.top.style = "hidden",
              table.border.bottom.style = "hidden",
              row.striping.include_table_body = FALSE) %>%
  tab_style(style = list(
    cell_borders(sides = c("top", "bottom"), color = "#DEE2E5", weight = px(1)),
    cell_fill(color = "#ecf0f1")),
    locations = list(cells_row_groups())) %>%
  tab_style(
    style = list(cell_borders(sides = c("top", "bottom"), color = "#DEE2E5", weight = px(1))),
    locations = list(cells_body())) %>%
  cols_label(
    label    = "Name",
    download = "Download",
    preview  = "Preview")
```

