---
title: "COVID-19 Data Norway"
output:
  html_document
---
<script>
  $(document).ready(function(){
    $('[data-toggle="tooltip"]').tooltip(); 
  });
</script>

<h3 style = "color: #6f7d7e;margin-top:8px;t">Public data about the COVID-19-situation in Norway </h3>
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

### Motivation
The current state of publicly available data about the COVID-19-situtation in Norway is a mix of [PDF-reports](https://www.fhi.no/sv/smittsomme-sykdommer/corona/dags--og-ukerapporter/dags--og-ukerapporter-om-koronavirus/), [Excel-files](https://www.nav.no/no/nav-og-samfunn/statistikk/arbeidssokere-og-stillinger-statistikk/permitterte), [Power BI-dashboards](https://www.helsedirektoratet.no/statistikk/antall-innlagte-pasienter-pa-sykehus-med-pavist-covid-19) and public registries. Further, much of the data is only released as cumulative statistics at aggregated levels (e.g. [MSIS](http://www.msis.no/)). This has created a market for media outlets to release local "situation reports" behind paywalls (see: [Aftenposten](https://www.aftenposten.no/norge/i/K3mnr4/i-det-meste-av-landet-bremser-viruset-opp-i-oslo-sprer-det-seg-raskt-fra-bydel-til-bydel)). The motivation for this project is to collect disparate data sources of Covid-19 in Norway and make them freely available to the public in a timely and coherent manner.

### Use of data
All available data is free to use without attribution to this project. Media outlets are strongly encouraged to make their online-articles using this data publicly available.

### Contributing to the project
This project is a collaborative and voluntary effort and we would love your help. If you are an individual wishing to contribute, please read the [contribute section](contribute.html). If you are an organization interested in making your data available, please [get in touch](#).Test

```{r, message=FALSE, warning=FALSE, echo=FALSE}
library(gt)
library(tidyverse)
library(glue)
```

### Available data
```{r, echo=FALSE}
tribble(
  ~name, ~source, ~updated, ~category,
  "Infections", "MSIS", "2020-04-04", "Healthcare",
  "Deaths", "FHI", "2020-04-04", "Healthcare",
  "Admissions", "Helsedirektoratet", "2020-04-04", "Healthcare",
  "Temporary Layoffs", "NAV", "2020-04-04", "Economic") %>% 
  mutate(latest = '<a href = "#">csv</a> <a href = "#">xlsx</a>') %>%
  mutate(complete = '<a href = "#">csv</a> <a href = "#">xlsx</a>') %>% 
  mutate(preview = '<a href = "#"><span class="fa fa-search"></a>') %>% 
  mutate_at(vars(latest, complete, preview), map, htmltools::HTML) %>% 
  gt(groupname_col = "category") %>%
  tab_options(table.width = pct(100),
              table.border.top.style = "hidden",
              table.border.bottom.style = "hidden",
              row.striping.include_table_body = FALSE) %>%
  #tab_spanner(label = "Downlodad", columns = vars(latest, complete, preview)) %>% 
  tab_style(style = list(
    cell_borders(sides = c("top", "bottom"), color = "#DEE2E5", weight = px(1)),
    cell_fill(color = "#ecf0f1")),
    locations = list(cells_row_groups())) %>%
  tab_style(
    style = list(cell_borders(sides = c("top", "bottom"), color = "#DEE2E5", weight = px(1))),
    locations = list(cells_body())) %>%
  cols_label(
    name   = "Name",
    source = "Source",
    updated = "Updated",
    latest = "Latest",
    complete = "Complete",
    preview = "Preview")
```
<br>

### Supporting data
Lookup tables and maps for use with the available data sets.
```{r, echo=FALSE}
tribble(
  ~name, ~category,
  "Municipalities and Districts", "Lookup tables",
  "Municpialities", "Lookup tables",
  "MSIS-regions", "Lookup tables",
  "Municipalities and Districts", "Maps",
  "Municpialities", "Maps",
  "MSIS-regions", "Maps") %>%
  mutate(download = '<a href = "#">csv</a> <a href = "#">xlsx</a>',
         preview  = '<a href = "#"><span class="fa fa-search"></a>') %>% 
  mutate_at(vars(download), ~ifelse(category != "Maps", .x, '<a href= "#">geojson</a>')) %>% 
  mutate_at(vars(download, preview), map, htmltools::HTML) %>% 
  gt(groupname_col = "category") %>%
  tab_options(table.width = pct(100),
              table.border.top.style = "hidden",
              table.border.bottom.style = "hidden",
              row.striping.include_table_body = FALSE) %>%
  #tab_spanner(label = "Downlodad", columns = vars(latest, complete, preview)) %>% 
  tab_style(style = list(
    cell_borders(sides = c("top", "bottom"), color = "#DEE2E5", weight = px(1)),
    cell_fill(color = "#ecf0f1")),
    locations = list(cells_row_groups())) %>%
  tab_style(
    style = list(cell_borders(sides = c("top", "bottom"), color = "#DEE2E5", weight = px(1))),
    locations = list(cells_body())) %>%
  cols_label(
    name   = "Name",
    download = "Download",
    preview = "Preview")
```